Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
DSN changes

\linespread{1.05}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figs/graph-clique-crop.pdf}
\caption{Clique and pseudo-clique neighborhoods associated with
  unit distance neighborhoods of Dobbertin and Kasselman collision
  classes from the literature.}
\label{Fig:Graph-Clique}
\end{center}
\end{figure}

@@

In this section we present our empirical results, evaluating the
utility of existing published collisions by exploring their structure
with 3-CNF-SAT, and building representative neighborhoods using our
distance metrics.  We present these results in the form of an
exploration of unique differentials, exploration of unit distance
neighborhoods, maximum count of zeros in the binary representation of
a colliding block, the existance of blocks which collide under
multiple initial values, and ASCII block collisions as discussed
previously in Section \label{Sec:Intuition}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figs/graph-neighborhood-crop.pdf}
\caption{All collisions in the unit distance neighborhoods of
  Dobbertin and Kasselman collision classes
  organized by connectedness, and showing the inter-distance
  paths neighborhoods of unpublished collisions.}
\label{Fig:Graph-Neighborhood}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figs/families48.pdf}
\caption{A visualization of the unit-distance family relationships
of the 35,000 new collisions in MD4. }
\label{Fig:Families48}
\end{center}
\end{figure}

>>>>

\linespread{1.04}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{Figs/graph-clique-crop.pdf}
\caption{Clique and pseudo-clique neighborhoods associated with
  unit distance neighborhoods of Dobbertin and Kasselman collision
  classes from the literature.}
\label{Fig:Graph-Clique}
\end{center}
\end{figure*}

@@

In this section we present our empirical results, evaluating the
utility of existing published collisions by exploring their structure
with 3-CNF-SAT, and building representative neighborhoods using our
distance metrics.  We present these results in the form of an
exploration of unique differentials, exploration of unit distance
neighborhoods, maximum count of zeros in the binary representation of
a colliding block, the existance of blocks which collide under
multiple initial values, and ASCII block collisions as discussed
previously in Section \ref{Sec:Intuition}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{Figs/graph-neighborhood-crop.pdf}
\caption{All collisions in the unit distance neighborhoods of
  Dobbertin and Kasselman collision classes
  organized by connectedness, and showing the inter-distance
  paths neighborhoods of unpublished collisions.}
\label{Fig:Graph-Neighborhood}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{Figs/families48.pdf}
\caption{A visualization of the unit-distance family relationships
of the 35,000 new collisions in MD4. Note these nodes represent
collision \textbf{families} with solid vertices as opposed to the
classes in previous figures represented by open verticies.}
\label{Fig:Families48}
\end{center}
\end{figure*}
